Current State of Knowledge Representation Systems for Robotics

### 2011-12-08 krs-survey.tex
After discussion with Moritz and Michael, removed subsections on benchmarking
Reworked organization of features list after talk with Moritz & Michael

\title{Current State of Knowledge Representation Systems for Robotics}
\author{Séverin Lemaignan, Moritz Tenorth}

@@

\subsection{Evaluation of a knowledge representation system}
\label{sect|evaluation}

\subsubsection{Desirable features of a knowledge representation system}
\label{sect|evaluation-literature}

@@

\subsubsection{Benchmarking}
\label{sect|benchmarking}

\cite{Hawes2008}: benchmarking of "Information-Processing Architectures on Intelligent Systems"
\subsubsection{Psychological tests}
\label{sect|evaluation-tests}

\begin{itemize}
	\item Language comprehension tests: Token Test~\cite{DiSimoni1978}
\end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{The Cognitive Scenario}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Compared Features}
\label{sect|features}

\subsection{What Can be Represented? The Expressiveness Question}
\label{sect|intrinsic-features}

%\subsubsection{Expressiveness}
%\label{sect|expressiveness}

@@

\subsubsection{Representation of time}

@@

@@

\subsubsection{Introspection: what can I do?}
\label{sect|introspection}

\paragraph{General introspection}

Modelling of the robot capabilities.

\paragraph{Meta-cognition: knowledge on the knowledge}

%%%%%%%%%%
\subsection{Reasoning Techniques}

@@

\subsubsection{Prediction and projection and diagnosis tasks}
\label{sect|prediction-projection}

@@

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Underlying knowledge model}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Surveyed systems}

>>>>

\title{Current State of Knowledge Representation Systems for Robotics}
\author{Séverin Lemaignan, Moritz Tenorth, Michael Beetz}

@@

\subsubsection{What to expect from a knowledge representation system}
\label{sect|evaluation-literature}

@@

\cite{Hawes2008}: benchmarking of "Information-Processing Architectures on Intelligent Systems"

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A Prototypical Scenario}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{A taxonomy of features of knowledge representation systems}
\label{sect|features}

\subsection{Expressiveness: What Can be Represented?}
\label{sect|expressiveness}

@@

\subsubsection{Meta-cognition: knowledge on the knowledge}

%%%%%%%%%%
\subsection{How things are represented?}
\label{sect|higher-level-domain-representation}

\subsubsection{Spatio-Temporal Representations}

\paragraph{Representation of time}

@@

\paragraph{Representation of space}

\paragraph{Representation of events and actions}

@@

\subsubsection{Introspection: Who am I? What can I do?}
\label{sect|introspection}

\paragraph{The introspective robot}

\paragraph{Modelling of the robot capabilities}

%%%%%%%%%%
\subsection{Reasoning Techniques}
\label{sect|reasoning}

@@

\subsubsection{Prediction, projection and diagnosis tasks}
\label{sect|prediction-projection}

@@

\subsubsection{Integration with sensori-motor layers}
\label{sect|integration-sensorimotor}

Ability to ``listen'' to the robot internal structures.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Knowledge instanciation}

How much knowledge is available? Which content? How big is the knowledge base?

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Surveyed systems}
\label{sect|surveyed-systems}
